\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-10-30 paper/main.tex
checking in edits (workiing on integrating R1 responses into paper)

Our understanding of how we form situation models and schemas, and how they
interact with our subjective experiences and memories, is constrained in part
by substantial differences in how we study these processes. Situation models
and schemas are most often studied using ``naturalistic'' stimuli such as
narratives and movies~\citep{ZwaaEtal95,ZwaaRadv98, NastEtal20}. In contrast,
our understanding of how we organize our memories has been most widely informed
by more traditional paradigms like free recall of random word
lists~\citep{Kaha12, Kaha20}. In free recall, participants study lists of items
and are instructed to recall the items in any order they choose. The orders in
which words come to mind can provide insights into how participants have
organized their memories of the studied words. Because random word lists are
unstructured by design, it is not clear if, or how, non-trivial situation models
might apply to these stimuli. Nevertheless, there are \textit{some}
commonalities between memory for word lists and memory for real-world
experiences.

@@

>>>>

Our understanding of how we form situation models and schemas, and how they
interact with our subjective experiences and memories, is constrained in part
by substantial differences in how we study these processes. Situation models
and schemas are most often studied using ``naturalistic'' stimuli such as
narratives and movies~\citep{ZwaaEtal95,ZwaaRadv98, NastEtal20}. In contrast,
our understanding of how we organize our memories has been most widely informed
by more traditional paradigms like free recall of random word
lists~\citep{Kaha12, Kaha20}. In free recall, participants study lists of items
and are instructed to recall the items in any order they choose. The orders in
which words come to mind can provide insights into how participants have
organized their memories of the studied words. Because random word lists are
unstructured by design, it is not clear if, or how, non-trivial situation
models might apply to these stimuli. As we unpack below, this provides an
important motivation for our current study, which uses free recall of
\textit{structured} lists to help bridge the gap between these two lines of
research.

@@

% define the theoretical stakes of our study

From a theoretical perspective, we are interested in several core questions
organized around the central theme of how structure in our experiences affect
how we remember \textit{those} experiences, and also how we remember
\textit{future} experiences (which may or may not exhibit similar structure).
For example, when we distill participants' experiences down to simple word
lists that vary (meaningfully) along just a few feature dimensions, are there
important differences in which dimenesions influence participants' memories? Or
are all features essentially ``equally'' influential? Further, are there
differences in how specific features influence participants' memories for
ongoing versus future experiences? Are there interaction effects between
different features, or do people appear to treat each feature independently?
Finally, are there individual differences in how people organize their
memories, or in how people are influenced by our experimental manipulations? If
so, what are those differences and which aspects of memory do they affect?
